\section{Results}\label{results}

The computation of RR-index in our dataset with the dimensions
\emph{h} -index, \emph{A} and \emph{PI}, i.e., \emph{RR(h, A, PI),}
produces a classification into \textasciitilde{}700 levels of skylines.
In Figure 2 the size of each skyline level is illustrated. The plot
follows a relatively stable distribution with about 200 authors per
skyline level and a peak at level 500. The first 20 skyline levels are
signifi­cantly smaller in size (less than 50 entities per skyline
level); the same applies for the last sky­line levels (higher than 600).
This observation indicates that when a unified relative ranking is
produced though comparison with one's peers the ``Matthew effect'' in
scientific output is mi­tigated in the sense that few scientists are
ranked at the top, but also few of them are assigned at the lowest
ranks. The majority of them are dispersed across the moderate skyline
levels, which better explains the actual distribution of performance .
Please, note that Table 2 gives abbreviations for the tested RR-indices.

In a similar manner, Figure 3 shows the distribution of skyline sizes
for \emph{RR(h, A, PI, h\textsuperscript{t}).} In this computation we
added the dimension of trend \emph{h}-index
(\emph{h\textsuperscript{t}}). The trend \emph{h}-index is clustered
very close to the original \emph{h}-index. We argue that this happened
due to the fact that Computer Science, the domain selected, is a
relatively new and fast paced field, where not enough ``slee­ping
beauties'' are present or even when they do exist, they do not ``sleep''
for long periods of time. Therefore, the addi­tion of the trend index
will help assign merit to scientists publishing in up and coming fields
of research. With one added dimension, we see that the levels of
skylines decreased and sky­line sizes increased. However, in the total
ranking, the similarity of \emph{RR(d1)} and \emph{RR(d3)} is still very
high (0.997 Spearman, 0.957 Kendall tau), as shown later in Table 3 and
Table 4 . This means that, although we added a new dimension, the number
of levels and the ties changed but the ranking remains almost the same.